### 2021-04-26 spanish/sections/experience.tex
Update experience.tex

\begin{cventries}
\cventry
{Instructor} 
{Universidad de Santiago de Chile} 
{Santiago, Chile} 
{2019 - en comisión}
{Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}

>>>>

\begin{cventries}
\cventry
{Profesor Instructor} 
{Universidad de Santiago de Chile} 
{Santiago, Chile} 
{2019 - en comisión}
{Departamento de Gestión y Políticas Públicas, Facultad de Administración y Economía}\vspace{1.5mm}
